### 2020-02-17 thesis/pretext.tex
added abstract and some data.

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
presented on \underline{\jpsays{include the correct date here!}}.
\vspace{1.0cm}

@@

\justify{}
\doublespacing
"Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et
dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip
ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore 
eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia
deserunt mollit anim id est laborum."

\iffalse
\singlespacing
"Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt..."
\fi

@@

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented October 26, 2019  \\
Commencement December 2019 \jpsays{include the correct date here!}
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\jpsays{get the date right here? August 26, 2015}. \\

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
"Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et
dolore magna aliqua. Ut

>>>>

\justify{}
\underline{Jordan K. Pommerenck} for the degree of \underline{Doctor of Philosophy} in \underline{Physics}
presented on \underline{\jpsays{include the correct date here FORMAT = April 10, 2020!}}.
\vspace{1.0cm}

@@

\justify{}
\doublespacing
This work introduces the development of the novel flat-histogram Monte 
Carlo (MC) method SAD and explores the convergence properties of a 
variety of related weight-based MC methods. The new method is applied 
to a variety of physical `test' systems including the 2D Ising model, 
square-well fluid, and Lennard-Jones clusters. A driving motivation for 
developing novel Monte Carlo methods that have physically based tunable 
parameters is to provide simulation methods for exploring metal-organic 
frameworks (MOFs). A theoretical framework for gas adsorption and 
delivery in metal-organic frameworks is developed and compared with 
experimental data. SAD is a introduced as a powerful method for 
examining thermodynamic properties for MOFs.  A \emph{preliminary} 
groundwork is laid for the future development of 2D SAD which would be 
able to compute isotherms for any given MOF thereby providing a 
powerful way for researchers to determine a MOF's suitability for gas 
storage applications.

@@

\vspace{1.0cm}
by \\
Jordan K. Pommerenck \\
\vspace{3.0cm}
A DISSERTATION \\
\vspace{0.5cm}
submitted to \\
\vspace{0.5cm}
Oregon State University \\
\vspace{3.0cm}
in partial fulfillment of \\
the requirements for the \\
degree of \\
\vspace{1.0cm}
Doctor of Philosophy \\
\vspace{3.0cm}
Presented April 10, 2020  \\
Commencement June 2020 \jpsays{include the correct date here!}
\end{center}

\newpage{}
\thispagestyle{empty}
\singlespacing
\justify{}
\underline{Doctor of Philosophy} dissertation of \underline{Jordan K. Pommerenck} presented on
\jpsays{get the date right here? April 10, 2015}. \\

@@

\newpage{}
\thispagestyle{empty}
\begin{center}
	\large
	ACKNOWLEDGEMENTS
\end{center}
\justify{}
\doublespacing
\jpsays{FIXME: "Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et
dolore magna aliqua. Ut}
